---
title: "Mapping Lebanon"
author: "Daniel K Baissa"
date: "2/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())

library(tidyverse)
library(sf)
library(googleway)
library(jsonlite)
library(mapview)
```

## Intro

My goal in the document is to merge the data from the Voter Database of Lebanon scrapped by David and merge it to a shapefile. We tried matching via admin3 in Arabic and for whatever reason, there was a lot of missing data. Therefore my strategy is to brute force it by searching for each location via the Google api and the googleway library.

I will start by loading the the libraries


Now let's load in the data

```{r data, message=FALSE, warning=FALSE}
Lebanon_shp <- st_read("Data/Lebanon Shapes/lbn_admbnda_adm3_cdr_20200810.shp")
st_transform(Lebanon_shp, 4326)

Lebanon_shp2 <- st_read("Data/Cammett_data/voter_nation.shp")
st_transform(Lebanon_shp2, 4326)

votreg_full <- readRDS("Data/Voter_Data/votreg_full.RDS")
Lat_Long_votreg_best_matches <- read_csv("Data/Googled_Data/Lat_Long_votreg_best_matches_full.csv")
Lat_Long_votreg_next_best_matches <- read_csv("Data/Googled_Data/Lat_Long_votreg_next_best_matches_full.csv")
```
### Comparing shapefiles

Now that the data is loaded I will compare shapefiles to see how well they match. Hopefully the one with Arabic matches the older shapefile compelety 

```{r}
ggplot(data = Lebanon_shp) +
  geom_sf(color = 'red', alpha = 0) +
  theme_classic()+
  geom_sf(data = Lebanon_shp2, color = 'black', alpha = 0) 
```

It looks pretty close but not perfect. Its actually pretty bad to the south. For now let's zoom in to see how bad it might really be.

```{r}

ggplot(data = Lebanon_shp) +
  geom_sf(color = 'red', alpha = 0) +
  theme_classic()+
  geom_sf(data = Lebanon_shp2, color = 'black', alpha = 0) +
   # coord_sf(xlim = c(35.45, 35.55), ylim = c(33.85, 33.95), expand = TRUE)+
  coord_sf(xlim = c(35.55, 35.65), ylim = c(33.9, 34), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```

```{r}

ggplot(data = Lebanon_shp) +
  geom_sf(color = 'red', alpha = 0) +
  theme_classic()+
  geom_sf(data = Lebanon_shp2, color = 'black', alpha = 0) +
   coord_sf(xlim = c(35.2, 35.8), ylim = c(33.5, 33.95), expand = TRUE)+
  # coord_sf(xlim = c(35.55, 35.65), ylim = c(33.9, 34), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```

Its surprisingly good.

Now let's look at the south. Since that is where most of the issues are.

```{r}
ggplot(data = Lebanon_shp) +
  geom_sf(color = 'red', alpha = 0) +
  theme_classic()+
  geom_sf(data = Lebanon_shp2, color = 'black', alpha = 0) +
   coord_sf(xlim = c(35, 35.8), ylim = c(33, 33.5), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```

It's not as bad as I expected, but not great... But given that the shapefile I have has Arabic text, I can at least merge on that. Then I can figure out how to deal with the areas that did not match.

## Aggregating the Data

Now that we know what the data look like we can start aggregating by admin 3 level. I will also add some population percentage variables while doing this.

Let's start by looking for cases where there are only a handful of people from an area

```{r}
votreg_full %>%
  group_by(adm_03_ar) %>%
  summarise(Population_Local = n()) %>% 
  ungroup %>% 
  distinct(adm_03_ar, .keep_all = TRUE) %>% 
  select(Population_Local, adm_03_ar) %>% 
  ggplot() +
  geom_col(aes(x = reorder(adm_03_ar, -Population_Local), y = Population_Local))
```

It looks like there are several places where only a handful of people regestered.

```{r}
votreg_full %>%
  group_by(adm_03_ar) %>%
  summarise(Population_Local = n()) %>% 
  ungroup %>% 
  distinct(adm_03_ar, .keep_all = TRUE) %>% 
  select(Population_Local, adm_03_ar) %>% 
  filter(Population_Local < 50)
```


```{r}

df <- votreg_full %>%
  group_by(sect_en, adm_03_ar) %>%
  summarise(Population_Local = n()) %>%
  ungroup() %>%
  group_by(adm_03_ar) %>%
  mutate(Percentage_Local = (Population_Local/sum(Population_Local))*100) %>%
  ungroup() %>% 
  pivot_wider(names_from = sect_en, values_from = c(Percentage_Local, Population_Local))


```




Now I will merge the data on admin 3 matches.

```{r}
df_final <- merge(df, Lebanon_shp, by.y = "admin3Na_1", by.x = "adm_03_ar", all.x = TRUE)

df_final <- st_as_sf(df_final)
```

There are `r length(na.omit(df_final$admin3Name))` complete cases when merging the data with the shapefile that contains Arabic


Let's map the matches from the voter data to the shapefile vs not matches.

```{r}
ggplot(data = Lebanon_shp) +
  geom_sf(color = 'black', alpha = 0) +
  theme_classic()+
  geom_sf(data = df_final, fill = 'red', alpha = 1) 
```

The areas in red are the areas that matched.

Now let's at the admin 3 places that did not match and see if any of the best matches line up with these areas.

### Matches with admin 2 and admin3


When using the Googleway library I searched with the criteria of admin3, admin2, and Lebanon. Therefore, these should be the best matches. This resulted in `r length(na.omit(Lat_Long_votreg_best_matches$lat))` matches. The matches make up `r length(na.omit(Lat_Long_votreg_best_matches$lat))/length(Lat_Long_votreg_best_matches$lat)*100`% of all cases. 

Now let's make sure that there are no strange coordinates. When working with the RA Jana, we found some places may not be in Lebanon. So I will double check everything at every step.


```{r}

first_miss <- df_final %>% 
  filter(is.na(Shape_Area))

first_miss_df <- merge(first_miss, Lat_Long_votreg_best_matches, by.y = "adm_03_ar", by.x = "adm_03_ar", all.x = TRUE)

length(na.omit(first_miss_df$lat))
sum(is.na(first_miss_df$lat))

```
Using the Google best matches data, there are `r length(na.omit(first_miss_df$lat))` matches with the unmatched shapefile data. This leaves `r sum(is.na(first_miss_df$lat))` NAs. This means we have a total of `r length(na.omit(df_final$admin3Name)) + length(na.omit(first_miss_df$lat))` complete cases, or `r (length(na.omit(df_final$admin3Name)) + length(na.omit(first_miss_df$lat)))/length(df$adm_03_ar)`% of all of the admin 3 data.



```{r message=FALSE, warning=FALSE}


mapview(na.omit(Lat_Long_votreg_best_matches), xcol = "lon", ycol = "lat", crs = 4269, grid = FALSE)


```


These seem to have worked. Now I will see how these coordinates map onto the shapefile.

Let's start by assuming the matches actually match and see how this helps.

```{r}
ggplot(data = Lebanon_shp) +
  geom_sf(color = 'black', alpha = 0) +
  theme_classic()+
  geom_sf(data = df_final, fill = 'red', alpha = 1) +
  geom_point(data = first_miss_df, aes(y = lat, x = lon), color = 'blue')
   
  
  
  # geom_sf(data = df_final, fill = 'red', alpha = 1) +
  # geom_sf(data = first_miss_sf, fill = 'blue', alpha = 1)
  
```

```{r}
ggplot(data = Lebanon_shp) +
  geom_sf(color = 'black', alpha = 0) +
  theme_classic()+
  geom_sf(data = df_final, fill = 'red', alpha = 1) +
  geom_point(data = first_miss_df, aes(y = lat, x = lon), color = 'blue')+
   coord_sf(xlim = c(35.45, 35.55), ylim = c(33.85, 33.95), expand = TRUE)+
  xlab("")+ylab("")
```

Now let's see which shapes the searched data account for

```{r}

st_contains(Lebanon_shp, y, sparse = TRUE, prepared = TRUE, ..., model = "open")
```



```{r message=FALSE, warning=FALSE}
ggplot(data = Lebanon_shp) +
  geom_sf() +
  geom_point(data = Lat_Long_votreg_best_matches, aes(y = lat, x = lon), color = 'red') +
    coord_sf(xlim = c(35, 36.65), ylim = c(33, 34.75), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```

It almost looks like there might be several points per admin 3 zone. So I will zoom in the map in a few places to check.

```{r message=FALSE, warning=FALSE}
ggplot(data = Lebanon_shp) +
  geom_sf() +
  geom_point(data = Lat_Long_votreg_best_matches, aes(y = lat, x = lon), color = 'red') +
   coord_sf(xlim = c(35.45, 35.55), ylim = c(33.85, 33.95), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```


```{r message=FALSE, warning=FALSE}
ggplot(data = Lebanon_shp) +
  geom_sf() +
  geom_point(data = Lat_Long_votreg_best_matches, aes(y = lat, x = lon), color = 'red') +
   coord_sf(xlim = c(35.55, 35.65), ylim = c(33.9, 34), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```

For the most part the coordinates map on well. However, there are some cases where there are multiple points in a single admin 3 shape. Maybe this is because the district boundries changed?

### Matches without admin 2

After searching for the locations with both the admin 2 and admin 3 critera, I searched the remaining misses with just the admin 3 name and Lebanon. This resulted in an additional `r length(na.omit(Lat_Long_votreg_next_best_matches$lat))` matches. Combinded with the best matches it accounts for `r (length(na.omit(Lat_Long_votreg_best_matches$lat))+ length(na.omit(Lat_Long_votreg_next_best_matches$lat)))/length(Lat_Long_votreg_best_matches$lat)*100`% of all cases. 

```{r message=FALSE, warning=FALSE}

mapview(na.omit(Lat_Long_votreg_next_best_matches), xcol = "lon", ycol = "lat", crs = 4269, grid = FALSE)

```

Now we see there are places outside of Lebanon showing up in the data.

These seem to have worked. Now I will see how these coordinates map onto the shapefile.

```{r message=FALSE, warning=FALSE}
ggplot(data = Lebanon_shp) +
  geom_sf() +
  geom_point(data = Lat_Long_votreg_next_best_matches, aes(y = lat, x = lon), color = 'red') +
  coord_sf(xlim = c(35, 36.65), ylim = c(33, 34.75), expand = TRUE)+
  theme_classic()+
  xlab("")+ylab("")
```

